Forecasting climate change impacts on plant population dynamics at large spatial extents: a test case with sagebrush (\emph{Artemisia}) species

### 2015-11-03 docs/appendix_a.Rmd
updates model table

| Modeling Center | Model | Institution |
| --------------- | ----- | ----------- |
| BCC | BCC-CSM1.1 | Beijing Climate Center, China Meteorological Administration | 
| BCC | BCC-CSM1.1(m) | Beijing Climate Center, China Meteorological Administration | 
| CCCma | CanAM4 | Canadian Centre for Climate Modelling and Analysis |
| CCCma | CanCM4 | Canadian Centre for Climate Modelling and Analysis |
| CCCma | CanESM2 | Canadian Centre for Climate Modelling and Analysis |
| CCCMC | CMCC-CESM | Centro Euro-Mediterraneo per I Cambiamenti Climatici |
| CCCMC | CMCC-CM | Centro Euro-Mediterraneo per I Cambiamenti Climatici |
| CCCMC | CMCC-CMS | Centro Euro-Mediterraneo per I Cambiamenti Climatici |
| CNRM-CERFACS | CNRM-CM5 | Centre National de Recherches Meteorologiques / |
|  |  | Centre Europeen de Recherche et Formation Avancees en Calcul Scientifique |
| CNRM-CERFACS | CNRM-CM5-2 | Centre National de Recherches Meteorologiques / |
|  |  | Centre Europeen de Recherche et Formation Avancees en Calcul Scientifique |
| COLA and NCEP | CFSv2-2011 | Center for Ocean-Land-Atmosphere Studies and |
|  |  | National Centers for Environmental Prediction |
| CSIRO-BOM | ACCESS1.0 | CSIRO (Commonwealth Scientific and Industrial Research |
|  |  | Organisation, Australia), and BOM (Bureau of Meteorology, Australia) |

>>>>

| Modeling Center | Model | Institution |
| --------------- | ----- | ----------- |
| BCC | BCC-CSM1.1 | Beijing Climate Center, China Meteorological Administration | 
| BCC | BCC-CSM1.1(m) | Beijing Climate Center, China Meteorological Administration | 
| CCCma | CanAM4 | Canadian Centre for Climate Modelling and Analysis |
| CCCma | CanCM4 | Canadian Centre for Climate Modelling and Analysis |
| CCCma | CanESM2 | Canadian Centre for Climate Modelling and Analysis |
| CCCMC | CMCC-CESM | Centro Euro-Mediterraneo per I Cambiamenti Climatici |
| CCCMC | CMCC-CM | Centro Euro-Mediterraneo per I Cambiamenti Climatici |
| CCCMC | CMCC-CMS | Centro Euro-Mediterraneo per I Cambiamenti Climatici |
| CNRM-CERFACS | CNRM-CM5 | Centre National de Recherches Meteorologiques / |
|  |  | Centre Europeen de Recherche et Formation Avancees en Calcul Scientifique |
| CNRM-CERFACS | CNRM-CM5-2 | Centre National de Recherches Meteorologiques / |
|  |  | Centre Europeen de Recherche et Formation Avancees en Calcul Scientifique |
| COLA and NCEP | CFSv2-2011 | Center for Ocean-Land-Atmosphere Studies and |
|  |  | National Centers for Environmental Prediction |
| CSIRO-BOM | ACCESS1.0 | CSIRO (Commonwealth Scientific and Industrial Research |
|  |  | Organisation, Australia), and BOM (Bureau of Meteorology, Australia) |
| CSIRO-BOM | ACCESS1.3 | CSIRO (Commonwealth Scientific and Industrial Research |
|  |  | Organisation, Australia), and BOM (Bureau of Meteorology, Australia) |
